Constraint Grammar as a SAT problem

### 2015-06-01 paper/nodalida2015.tex
small stuff

\subsection{Time}

@@

\section{Applications}
\label{sec:apps}
As described in Section~\ref{sec:eval}, our implementation is not
competetive with the state of the art. It is more fruitful to focus on
things where the SAT-based representation can make an impact.
One such thing is grammar analysis\footnote{We thank Eckhard Bick for
  the suggestion.}.
There has been work on automatic tuning of hand-written CGs
\cite{bick2013tuning}, but to our knowledge, no tools which would
search for inconsistencies or unoptimal design in order to point it out to the grammar writer.

@@

The first rule selects the verb always, removing all other readings,
and the second rule removes verb reading, given certain condition.
If the rules are introduced in a different order, there is no
conflict: the REMOVE rule would not remove verb readings from all
possible verb analyses, so there is a possibility for the SELECT rule
to fire, as long as the input has verbs

Ordered SAT-CG can be used to detect conflicts without any
modifications, as a side effect of its design. 
After applying each rule, it stores the clauses
produced by it and commits to them---even if the new rules cannot
change the earlier decisions, the SAT solver still retains the
dependencies.
Given that each application of a rule gets a variable,
in case of a conflict, the program detects the particular
application that violates the previous clauses, with the sentence
where it is applied. Thus we get feedback which rule fails, and on which
particular word(s).

>>>>

\subsection{Execution time}

@@

\section{Applications}
\label{sec:apps}
As demonstrated in Section~\ref{sec:eval}, our implementation is not
competetive with the state of the art. It is more fruitful to focus on
things where the SAT-based representation can make an impact.
One such thing is grammar analysis\footnote{We thank Eckhard Bick for
  the suggestion.}.
There has been work on automatic tuning of hand-written CGs
\cite{bick2013tuning}, but to our knowledge, no tools which would
search for inconsistencies or unoptimal design in order to point it out to the grammar writer.

@@

The first rule selects the verb always, removing all other readings,
and the second rule removes verb reading, given certain condition.
If the rules are introduced in a different order, there is no
conflict: the REMOVE rule would not remove verb readings from all
possible verb analyses, so there is a possibility for the SELECT rule
to fire.

Ordered SAT-CG can be used to detect these conflicts without any
modifications, as a side effect of its design. 
After applying each rule, it stores the clauses
produced by it and commits to them
% ---even if the new rules cannot
% change the earlier decisions, the SAT solver still retains the
% dependencies.
% Given that each application of a rule 
% is 
% gets a variable,
In case of a conflict, the program detects the particular rule that 
violates the previous clauses, with the sentence
where it is applied. Thus we get feedback which rule fails, and on which
particular word(s).
